Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-11-17 special-issue-ci/volunteer-clouds-ieee-ci-si.tex
Some corrections

\subsubsection{Setup of Rastrigin's experiment in NodIO-W$^2$ }
This experiment was deployed in a virtual private server with 512MB of memory
runing Ubuntu OS version 14.04 and hosted in DigitalOcean.com. Unlike previous
experiments where the optimum was espected to be found many times, 
this problem was expected to run constantly for many days finding only
sub-optimal aproximations. In order to achieve this, the only change needed 
in the system was to limit the number of chromosmes kept in the pool. 
Previously, every PUT request which included a new chromose increased 
the size of the pool, in a long-running experiment this has to be avoided
in order to not exahust the available memory. In this experiment the size
of a chromosme was 1000 double precision numbers, considereing this
and the memory available in the server, the the pool was limited 
to 10,000 chromosomes.  In order to keep this size
constant a random chromosme was pulled out of the pool before inserting a
new one, when the pool was full. For this problem NodEO's \tt{ chromosme-float } 
and \tt{ classic-ea-float} modules where used. The parameters for the ea algorithm 
were tournament size = 3 and  population size = 500, returning exchanging a
chromosme with the server every 100 generations. Again two workers in each window.
As before, a few participation calls were published in throu posts in social networks.

>>>>

\subsubsection{Setup of Rastrigin's experiment in NodIO-W$^2$ }
This experiment was deployed in a virtual private server with 512MB of memory
runing Ubuntu OS version 14.04 and hosted in DigitalOcean.com. Unlike previous
experiments where the optimum was espected to be found many times, 
this problem was expected to run constantly for many days finding only
sub-optimal aproximations. In order to achieve this, the only change needed 
in the system was to limit the number of chromosmes kept in the pool. 
Previously, every PUT request which included a new chromose increased 
the size of the pool, in a long-running experiment this has to be avoided
in order to not exahust the available memory. In this experiment the size
of a chromosme was 1000 double precision numbers, considereing this
and the memory available in the server, the the pool was limited 
to 10,000 chromosomes.  In order to keep this size
constant a random chromosme was pulled out of the pool before inserting a
new one, when the pool was full. For this problem NodEO's \tt{ chromosme-float } 
and \tt{ classic-ea-float} modules were used. The parameters for the ea algorithm 
were tournament size = 3 and  population size = 500, returning exchanging a
chromosme with the server every 100 generations. Again two workers in each window.
As before, a few participation calls were published in social networks.
